### 2014-03-14 docs/paper.tex
Use correct bib in paper.tex.
Make it more clear, the two kinds of blocking.

Broadly speaking, there are two main challenges to proxy-based circumvention.
The first is obfuscation: making circumvention traffic difficult to distinguish
from traffic the censor wishes to allow. The second is proxy address
unblockability: making it difficult for the censor simply to block proxies by
address. Past works have considered one or both of these problems.

@@

\bibliographystyle{plain}  
\bibliography{related-work}

>>>>

Broadly speaking, there are two main challenges to proxy-based circumvention:
blocking by content and blocking by endpoint.
Blocking by content means that the censor inspect packet or flow payloads,
looking, for example, for forbidden protocols or keywords.
Content-based blocking is countered by obfuscation:
making circumvention traffic difficult to distinguish
from traffic the censor wishes to allow.
Blocking by endpoint means that the censor forbids all communication with certain
network addresses, whatever the content of the communication.
The challenge of endpoint blocking is met by making it difficult for the censor to learn proxy addresses;
by having sufficiently many proxies;
or by colocating proxies with high-value services, to block which would incur collateral damage.
Effective proxy-based circumvention requires that both these challenges be addressed.

@@

\bibliographystyle{plain}  
\bibliography{paper}
